# Word cloud for website

Code from [here](http://blog.fellstat.com/?cat=11) and [here](https://towardsdatascience.com/create-a-word-cloud-with-r-bde3e7422e8a).

Color brewer options from [here](https://www.r-graph-gallery.com/38-rcolorbrewers-palettes.html).

```{r}
##install.packages(c("wordcloud","tm"),repos="http://cran.r-project.org")
```

```{r}
library(wordcloud)
##library(wordcloud2)
library(tm)
library(dplyr)
library("ggwordcloud")
library(stringr)
library(cowplot)
```

Download the data spreadsheet from [here](https://docs.google.com/forms/d/1wHtvO_CWXNTHPCZTR38lgv914Ez3csjYWyZgHHOAHQI/edit#responses) as a csv file and change name to `lab-info.csv`.

Then, we read the file:
```{r}
df = read.csv("lab-info.csv", header=TRUE)
colnames(df) <- c("timestamp", "name", "pronouns","datejoin", "languages", "programming", "major", "twitter", "bday")
str(df)
head(df)
```

```{r}
## Languages
raw <- gsub("[[:punct:]\n]","",df$languages)
raw2 <- strsplit(raw, " ")
raw3 <- unlist(raw2)
t = table(raw3)
tdat = as.data.frame(t)

set.seed(907)
tdat <- tdat %>%
  mutate(angle = 90 * sample(c(0, 1), n(), replace = TRUE, prob = c(60, 40)))
p1<-ggplot(tdat, aes(label = raw3, size=Freq, color=as.factor(Freq), angle=angle)) +
  geom_text_wordcloud_area(shape = "circle", eccentricity = 1, grid_margin=0) +
  #geom_text_wordcloud_area() +
  scale_size_area(max_size = 16) +
  #scale_color_gradient()+
  scale_colour_brewer(palette = "Set2") +
  theme_minimal()
```

```{r}
## Programming
raw <- gsub("[[:punct:]\n]","",df$programming)
raw2 <- strsplit(raw, " ")
raw3 <- unlist(raw2)
t = table(raw3)
tdat = as.data.frame(t)

s1<-c("c","C", "CC")

for (j in 1){ #here do for as many synonim vectors as created
  i<-get(paste("s",j,sep=""))
  b<-data.frame(raw3=i[1],Freq=sum(tdat$Freq[tdat$raw3 %in% i]))
  tdat<-tdat[!tdat$raw3 %in% i,]
  tdat<-rbind(tdat,b)
}

set.seed(204)
tdat <- tdat %>%
  mutate(angle = 90 * sample(c(0, 1), n(), replace = TRUE, prob = c(60, 40)))

p2<-ggplot(tdat, aes(label = raw3, size=Freq, color=as.factor(Freq), angle=angle)) +
  geom_text_wordcloud_area(shape = "circle", eccentricity = 1, grid_margin=0) +
  #geom_text_wordcloud_area() +
  scale_size_area(max_size = 16) +
  #scale_color_gradient()+
  scale_colour_brewer(palette = "Set1") +
  theme_minimal()
```

```{r}
## Major
raw <- gsub("[[:punct:]\n]","",df$major)
raw <- str_replace(raw,"Computer Science", "ComputerScience")
raw<- str_replace(raw,"Data Science", "DataScience")
raw<- str_replace(raw,"Wildlife Ecology", "WildlifeEcology")

raw2 <- strsplit(raw, " ")
raw3 <- unlist(raw2)
t = table(raw3)
tdat = as.data.frame(t)

set.seed(206)
tdat <- tdat %>%
  mutate(angle = 90 * sample(c(0, 1), n(), replace = TRUE, prob = c(60, 40)))

p3<-ggplot(tdat, aes(label = raw3, size=Freq, color=as.factor(Freq), angle=angle)) +
  geom_text_wordcloud_area(shape = "circle", eccentricity = 1, grid_margin=0) +
  #geom_text_wordcloud_area() +
  scale_size_area(max_size = 16) +
  #scale_color_gradient()+
  scale_colour_brewer(palette = "Set3") +
  theme_minimal()
```

```{r}
allpanels<-plot_grid(p1,p2,p3,ncol=3,rel_widths = c(2,2,5))
title <- ggdraw() + draw_label(paste("Lab composition",sep=""),fontface = 'bold',x = 0,  hjust = 0 ,color="deepskyblue4") +
  theme(plot.margin = margin(0, 0, 0, 0))
plot_grid( title, allpanels,  ncol = 1,
  # rel_heights values control vertical title margins
  rel_heights = c(0.1, 1)
)
ggsave("sl-lab-composition.pdf",width = 12, height = 6) ##14,6
